% the director ---------------------------
%
% -- front page
%
\playbookpage{%
%
% -- pg.1/2 col.1/3
%
\pbcommon{Director}%
{I didn't want the job of Director, didn't want the power.  But there were no other candidates.  Only me, always in the background, working my ass off.}%
{When you spend a point of luck, the Keeper will bring your duties into play.}%
%
}{% -- pg.1/2 col.2/3
%
\begin{pbsect}{THE DIRECTOR'S DUTIES}[]
You get to decide what your position has in store for you.  Pick how you were selected as Director of the Bureau, and what The Board and The Bureau are expecting of you, on the reverse side of the sheet.
\end{pbsect}
%
\moveexpembedded{four}{Director}
\brln
%
\textit{You get these two:}\\
%
\begin{move*}{I'm Here For A Reason}
There’s something The Board expects you to do.  Work out the details with the Keeper, based on your duties as director of the bureau.  You cannot die until it comes to pass.  If you \textbf{die in play}, then you must spend a luck point.  You will then, somehow, recover or be returned to life.  Once your task is done, or you use up all your luck, all bets are off.
\end{move*}%
\br[1mm]
%
\begin{move*}{Advisors}
When you consult your heads of staff about an ongoing situation, take +1 to \textbf{investigate a mystery}.
\end{move*}%
\br[3mm]
%
\textit{Then pick two of these:}\\
%
\begin{move}{The Big Entrance}
When you \textbf{make a commanding entrance into a situation}, roll +Cool.  On a 10+ everyone stops to watch and listen until you finish your opening speech.  On a 7-9 you pick one person or entity to stop, watch and listen until you finish talking.  On a miss, you’re marked as the biggest threat by all enemies who are present.
\end{move}%
\br[1mm]
%
\begin{move}{Trust Your Gut}
When you \textbf{consult your instincts} about what to do next, roll +Weird: On a 10 or more, the Keeper will tell where you should go. Wherever that is, it will be important. You get +1 ongoing on the way to this place. On a 7-9, the Keeper will tell you a general direction to go. Take +1 forward as you explore that. On a miss, your instincts lead you into danger.
\end{move}%
%
}{% -- pg.1/2 col.3/3
%
\begin{move}[]{Dutiful}
When your requirements as director of the bureau rear their ugly head, and you \textbf{act in accordance with your Duties} (either Bureau or Board), then mark experience and take +1 forward.
\end{move}%
\br[1mm]
%
\begin{move}{Resilience}
You heal faster than normal people.  Any time your harm gets healed, heal an extra point.  Additionally, your wounds count as 1-harm less for the purpose of the Keeper’s harm moves.
\end{move}%
\br[1mm]
%
\begin{move}{Hotline}
When you \textbf{make a call on the Hotline}, tell the Keeper whether you’re trying to reach the Board, a different astral entity, or hear the echoing thoughts of the recently deceased, and roll +Sharp.  On a 10+, they tell you something useful.  On a 7-9, they tell you something interesting, but it’s up to you to make it useful.
\end{move}
%
\begin{pbsect}{GEAR}
You can have protective gear worth 1-armour, if you want.  You have the service weapon, like any Director would.
\end{pbsect}%
\brln
%
\begin{pbsect}{THE SERVICE WEAPON}
Design your weapon by choosing a base, three forms, and a material.  Your Service Weapon always counts as a weakness against the entities you fight.
\end{pbsect}%
\br[2mm]
%
\optionsparen{Base}{choose 1}%
{Hilt (2-harm hand balanced),
Handgun (2-harm close reload)}%
\br[2mm]
%
\optionsblurb{Forms}%
{Take Grip and choose 2 more.  Only one form is active at a time.  The service weapon can instantly reconfigure from one form to another any time you are in physical contact with it.}%
    {Grip (+1 harm),
    Pierce (Ignore-armor),
    Spin (Messy),
    Shatter (Area),
    {Surge (Thrown, Explosive, Loud)}}%
%
}\pagebreak% -- back page
%
\playbookpage{%
%
% -- pg.2/2 col.1/3
%
\begin{blurbparen}{Material}{pick one}
{Finally, pick what material the service weapon is made from.  “steel”, “cold iron”, “silver”, “wood”, “stone”, “bone”, “teeth”, “obsidian”, or anything else you want.}
\end{blurbparen}
%
\begin{pbsect}{Your Duties as Director}
\optionsparen{How You Were Selected}{pick one}%
    {Found The Service Weapon,
    The Bureau Found You,
    Survived An AWE,
    The Last Director Trained You,
    Sought Out By An Astral Entity}
\brln
Then pick two Bureau and two Board tags for your duty to the agency from the lists below.  This is how The Bureau’s future will unfold.  It’s okay to pick contradictory tags: that means there is management strife between The Board and The Bureau.
\br[2mm]
When you \textbf{mark off a point of luck}, the Keeper will throw something from your duties at you.
\end{pbsect}%
\br[4mm]
%
\optionstwocolparen{The Bureau}{pick two}%
    {Things are better with you in charge,
    A favored inner circle,
    A bountiful threshold,
    A normal life,
    The Bureau before the Board,
    Succumb to the power,
    Unethical research,
    You must save everyone,
    Employee dissent,
    You can save the Bureau}
%
\optionstwocolparen{The Board}{pick two}%
    {Conspiracy,
    Your employees safety doesn’t matter,
    Enraged Altered Items,
    Sacrifice,
    The Board runs the Bureau,
    The source of the Paranormal,
    Obedience,
    Dissent in the astral plane,
    Nearing your retirement,
    No normal life}%
%
}{% -- pg.2/2 col.2/3
%
\optionsparen{Ratings}{pick one line}%
    {{Charm+2, Cool-1, Sharp+1, Tough+2, Weird-1},
    {Charm-1, Cool+2, Sharp+1, Tough+2, Weird-1},
    {Charm+1, Cool+2, Sharp+1, Tough+1, Weird-1},
    {Charm-1, Cool+1, Sharp+2, Tough-1, Weird+2},
    {Charm+1, Cool+2, Sharp-1, Tough-1, Weird+2}}
%
\introductions{Director}%
\brln
%
\history%
    {{You are close blood relations.  Ask them exactly how close.},
    {They are destined to be your replacement.  Tell them how this was revealed.},
    {You worked your way up through the Bureau together, and trust them totally.},
    {Romantically entangled.  Or fated to be romantically entangled.},
    {A rival at first, but you came to a working arrangement.},
    {They could have been the Director instead of you.  Tell them how they failed.},
    {You saved their life, back before they knew the paranormal was real.  Tell them what you saved them from.}}%
%
}{% -- pg.2/2 col.3/3
%
\levelingup
%
\improvementsonecol{%
    {Get +1 Charm, max +3.},
    {Get +1 Weird, max +3.},
    {Get +1 Cool, max +3.},
    {Get +1 Sharp, max +3.},
    {Get +1 Tough, max +3.},
    {Take another Director move.},
    {Take another Director move.},
    {Take a move from another playbook.},
    {Take a move from another playbook.},
    {Take another Service Weapon Form.}
}{%
    {Get +1 to any rating, max +3.},
    {Get back one used Luck point.},
    {Create a second Bureau Agent to play as well as this one.},
    {Mark two of the basic moves as advanced.},
    {Mark another two of the basic moves as advanced.},
    {Step down as Director: forfeit your Service Weapon and pick a new playbook.},
    {Appoint a new Director, give them the Service Weapon, and retire.}
}%
%
}%
% -- end playbook