%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Altered World Event of the Week is a Monster of the Week derivative.
%
% Much of the textual content in the playbooks is copied from the original playbooks,
% following approval by Michael Sands for the free distribution of the AWEotW document.
% See: https://genericgames.co.nz/third_party_policy/ for his third party policy.
%
% Re-use of this script is for personal reproduction of the formatting and generation
% of other custom playbooks.  Any reproduction of the text should seek approval per the
% aforementioned generic games third party policy.
%
% Monster of the Week is copyrighted by Evil Hat Productions, LLC and Generic Games.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% the investigator ---------------------------
%
% -- front page
%
\playbookpage{%
%
% -- pg.1/2 col.1/3
%
\pbcommon{Investigator}%
{Someone sends a handwritten letter about a stapler that growls and bites the other office supplies and I'm the one getting flown out to Minnesota to check it out.}%
{When you mark off a point of luck, the Keeper will haul out the department's red tape.}%
%
}{% -- pg.1/2 col.2/3
%
\moveexp{three}{Investigator}
\brln
%
\begin{move}{Connect the Dots}
At the beginning of each mystery, if you \textbf{look for the wider patterns} that current events might be part of, roll +Sharp.  On a 10+ hold 3, and on a 7-9 hold 1.  Spend your hold during the mystery to ask the keeper any one of the following questions:
\holdoptions%
    {Is this person connected to current events more than they are saying?,
    When and where will the next critical event occur?,
    What caused this paranormal occurrence?,
    Is this connected to previous mysteries we have investigated?,
    How does this mystery connect to the bigger picture?}%
\end{move}%
\br[1mm]
%
\begin{move}{Ockham’s Exposition}
When you \textbf{first encounter something strange}, you may ask the Keeper what sort of thing it is.  They will tell you if the cause is natural, a person, or the paranormal.  You gain +1 forward when dealing with it.
\end{move}%
\br[1mm]
%
\begin{move}{Suspicous Mind}
When you think someone is lying to you, tell the Keeper or that Agent, whomever plays the character.  They must tell you honestly if a lie was spoken, but are not required to point out the lie, nor are they required to tell you the truth.
\end{move}%
\br[1mm]
%
\begin{move}{Government Friends}
You know a lot of people in government institutions.  When you contact a \textbf{government friend to help} you with a mystery, roll +Charm.  On a 10+ they’re available and helpful - they can cover something up, provide clearance, get you special information, or provide protection.  On a 7-9 they’re prepared to help, but it’s either going to take some time or you’re going to have to do part of it yourself.  On a miss, you burn some bridges.
\end{move}%
%
}{% -- pg.1/2 col.3/3
%
\begin{move}[]{See, it all fits together}
You can use Sharp instead of Charm when you \textbf{manipulate someone}.
\end{move}%
\br[1mm]
%
\begin{move}{The Things I've Seen}
When you \textbf{encounter a paranormal entity or phenomenon}, you may declare that you have seen it before.  The keeper may ask you some questions about that encounter, and will then tell you one useful fact you learned and one danger you need to watch out for (maybe right now).
\end{move}%
\br[1mm]
%
\begin{move}{"Just One More Thing"}
When you \textbf{ask a suspect leading questions}, roll +Charm. On a 10+ hold 2, on a 7-9 hold 1, on a miss hold 1 but something bad is going to happen too. Spend your hold to ask questions from this list:
\holdoptions%
{Ask one question from the investigate a mystery list.,
Are they in control of themselves?,
What is something you left out that you didn’t want me to notice?,
Are you complicit with any ongoing paranormal activity?,
Did you have something to do with this event?}
\end{move}
%
}\pagebreak% -- back page
%
\playbookpage{%
%
% -- pg.2/2 col.1/3
%
\begin{pbsect}{GEAR}[]
You get two self defense items, and two investigation tools.
\end{pbsect}
\br[2mm]
%
\optionsparen{Self Defense Items}{choose two}%
    {Walking stick (1-harm hand innocuous),
    Small handgun (2-harm close reload loud),
    Small knife (1-harm hand messy),
    Martial arts training (1-harm hand innocuous),
    Incapacitating spray (0-harm hand irritating),
    Heavy flashlight (1-harm hand innocuous)}
\brln
%
\optionsparen{Investigation Tools}{choose two}%
    {Dowsing Rods,
    A CB Hand Radio attuned to only picks up paranormal wavelengths,
    {Black rock containment gear (mittens, tongs, a box with a locking lid)},
    Bag of film cameras and microphones,
    Paranormal measuring tools}%
%
\begin{pbsect}{DEPARTMENT RESOURCES}
The investigations department itself comes with its own perks and red tape.  Pick two perks that the department offers you while you're on the job, and a red tape issue you have to battle through to get the job done
\end{pbsect}
\br[2mm]
%
\optionsparen{Department Perks}{choose two}%
    {Well-financed,
    Rigorous training,
    Cover identities,
    Offices all over the place,
    Good intel,
    Recognized Authority}
\br[1pt]
%
\optionsparen{Department Red Tape}{choose one}%
    {Bureaucratic,
    Hostile superiors,
    Interdepartmental rivalry,
    Live capture policy,
    Trainee dumping ground}
%
}{% -- pg.2/2 col.2/3
%
\optionsparen{Ratings}{pick one line}%
    {{Charm+1, Cool+1, Sharp+2, Tough-1, Weird=0},
    {Charm=0, Cool+1, Sharp+2, Tough-1, Weird+1},
    {Charm+1, Cool-1, Sharp+2, Tough+1, Weird=0},
    {Charm+1, Cool-1, Sharp+2, Tough=0, Weird+1},
    {Charm-1, Cool-1, Sharp+2, Tough=0, Weird+2}}
%
\introductions{Investigator}%
\brln
%
\begin{history}
\begin{itemize}
\item  They’re somehow tied into it all. You’ve been keeping an eye on them.
\item  They’re a close relative. Ask them to decide exactly what.
\item  Old friends, who originally met through a long chain of coincidences.
\item  You're both members of the same support group.
\item The signs all pointed to working together. So you found them and now you work together.
\item They were involved in a supernatural event similar to your first encounter. Perhaps it was the same event, or perhaps you investigated their event later. Ask them how the event affected them.
\item You met when you were each investigating separate mysteries. Tell them what trick you used to protect them from weirdness and ask them how they saved you from a danger.
\end{itemize}
\end{history}
%
}{% -- pg.2/2 col.3/3
%
\levelingup
%
\improvementsonecol{%
    {Get +1 Charm, max +3.},
    {Get +1 Weird, max +3.},
    {Get +1 Cool, max +3.},
    {Get +1 Sharp, max +3.},
    {Take another Investigator move.},
    {Take another Investigator move.},
    {Take a move from another playbook.},
    {Get another resource tag for your agency or change a red tape tag.},
    {The Department assigns you a partner.  Use the Ranger’s Squad move to tag and describe them.}
}{%
    {Get +1 to any rating, max +3.},
    {Get back one used Luck point.},
    {Create a second Bureau Agent to play as well as this one.},
    {Mark two of the basic moves as advanced.},
    {Mark another two of the basic moves as advanced.},
    {Jump departments: change to a new playbook.},
    {Get promoted to the Head of Investigations.  This character becomes an NPC.  Start a new character.},
    {Retire to safety.}
}%
%
}%
% -- end playbook