% the outsider ---------------------------
%
% -- front page
%
\playbookpage{%
%
% -- pg.1/2 col.1/3
%
\pbcommon{Outsider}%
{You spend your life watching a movie, thinking that's all there is.  You only realize there's more to find when it reaches through the screen to grab you.}%
{When you spend a point of Luck, your first encounter comes up in play. It could be a flashback, new occurrence, or related event.}%
%
}{% -- pg.1/2 col.2/3
%
\moveexp{three}{Outsider}
\brln
%
\textit{You get this one:}
%
\br[2mm]
\begin{minipage}[t]{0.05\linewidth}
\checkedbox
\end{minipage}
%
\begin{minipage}[t]{0.94\linewidth}
\textbf{\normalsize First Encounter:}
One strange event started you down this path, sparking your need to discover the truth behind the unexplained. Decide what that event was: pick a category below and take the associated move. Then tell everyone what happened to you (or someone close to you).%
\br[1mm]
%
\begin{move}{AWE Survivor}
You take note of any reports of paranormal behavior. Whenever you first see a new type of AWE, you may immediately ask one of the \textbf{investigate a mystery} questions.
\end{move}%
\br[1mm]
%
\begin{move}{Non-Euclidean}
Things are not fixed. You never need \textbf{act under pressure} when supernatural forces alter the environment around you, and you get 2-armour against harm from sudden changes to the laws of physics
\end{move}%
\br[1mm]
%
\begin{move}{Astral Friend}
Something in the astral plane is looking out for you.  You start with 1 extra Luck: \checkbox
\end{move}%
\br[1mm]
%
\begin{move}{Strange Dangers}
You are always watching for hazards. When you have no armour, you still count as having 1-armour
\end{move}%
\br[1mm]
%
\begin{move}{Cosmic Insight}
You have peeked beyond the veil of this plane. You never need to \textbf{act under pressure} due to feelings of paranoia, despair, or isolation.
\end{move}%
\br[1mm]
%
\begin{move}{Bureau Interference}
Long ago, the Bureau took someone away who was special to you.  You’ve been trying to find them ever since.  Whenever \textbf{you directly confront someone} about them hiding information or evidence from you, they must do one of the following: give you the truth, bail out of the situation, or find a way to stop you from asking so damn many nosy questions, quick.  
\end{move}
%
\end{minipage}
%
}{% -- pg.1/2 col.3/3
%
\textit{Then pick two of these:}
%
\begin{move}{NEVER AGAIN}
In a dangerous situation, you may choose to \textbf{protect someone} without rolling, as if you had rolled a 10+, but you may not choose to “suffer little harm.”
\end{move}%
\br[1mm]
%
\begin{move}{DIY Surgery}
When you \textbf{do quick and dirty first aid} on someone (including yourself), roll +Cool. On a 10+ it’s all good, it counts as normal first aid, plus stabilize the injury and heal 1 harm. On a 7-9 it counts as normal first aid, plus one of these, your choice:
\holdoptions%
    {{Stabilize the injury but the patient takes -1 forward.},
    {Heal 1-harm and stabilize for now, but it will return as 2-harm and become unstable again later.},
    {Heal 1-harm and stabilize but the patient takes -1 ongoing until it’s fixed properly.}}
\end{move}%
\br[1mm]
%
\begin{move}{Often Overlooked}
When you \textbf{act all crazy} to avoid something, roll +Weird.  On a 10+ you’re regarded as unthreatening and unimportant.  On a 7-9, pick one: unthreatening or unimportant.  On a miss you draw lots (but not all) of the attention.
\end{move}%
\br[1mm]
%
\begin{move}{Its Not as Bad As It Looks}
Once per mystery \textbf{you may attempt to resist all paranormal influences} affecting you.  Roll +Cool.  On a 10+ heal 2 harm and you are resilient against anything paranormal, for a time.  On a 7-9 you may either break free of a paranormal influence, or heal 2 harm.  On a miss it’s worse than you thought, the paranormal influence takes over, the Keeper will say how.
\end{move}%
\br[1mm]
%
\begin{move}{Contrary}
When you \textbf{seek out and receive someone’s honest advice} on the best course of action for you and then do something else instead, mark experience. If you do exactly the opposite of their advice, you also take +1 ongoing on any moves you make pursuing that course.
\end{move}
%
\begin{move}{Fellow Believer}
You’re relatable in ways that other Agents aren’t.  People see you as a fellow conspiracy theorist, and are willing to open up to you about weird things they wouldn’t mention around other government agents.
\end{move}
%
}\pagebreak% -- back page
%
\playbookpage{%
%
% -- pg.2/2 col.1/3
%
\begin{pbsect}{GEAR}[]
You have protective wear, suited to your look, worth 1-armour, a 9mm (2-harm close loud) and a big knife (1-harm hand).
\end{pbsect}%
\br[2mm]
%
\optionsparen{Non-Bureau Approved Protection}{choose two}%
    {{\textbf{Tinfoil Hat:} while worn, you are shielded from direct paranormal influence on your mind.  You also look like a nut, and take -1 Charm ongoing.},
    {\textbf{Lead-lined Vest:} while worn, psychic harm against you cannot ignore armor.  You also insulate yourself from paranormal abilities, take -1 Weird ongoing.},
    {\textbf{Rubber Biohazard Suit:} while worn, and in good condition, you are protected from any biological effects such as molds and toxins.  You also have a difficult time moving, take -1 Tough ongoing.},
    {\textbf{Modified Welding Mask:} while worn, you are unaffected by paranormal effects triggered when looking at, or away from, something.  You have a difficult time seeing anything, really, and take -1 Sharp ongoing.},
    {\textbf{Resonance Cancelling Headphones:} while worn, auditory paranormal effects cannot affect you.  You barely hear normal sounds either, and take -1 Cool ongoing.}}%
\brln
%
\begin{pbsect}{EXPERT DRIVER}
You have +1 ongoing while driving.  Plus you can hotwire any vehicle (the older and more normal it is, the fewer tools you need to do it). You also have two vehicles of your own.
\optionsparen{Vehicle}{choose two}%
    {Classic motorcycle,
    Dirt Bike,
    Classic car,
    Nondescript car,
    Pickup truck,
    Cargo van,
    Minivan}
\end{pbsect}
%
}{% -- pg.2/2 col.2/3
%
\optionsparen{Ratings}{pick one line}%
    {{Charm=0, Cool+1, Sharp-1, Tough+2, Weird+1},
    {Charm=0, Cool=0, Sharp+1, Tough+2, Weird=0},
    {Charm+1, Cool=0, Sharp+1, Tough+2, Weird-1},
    {Charm-1, Cool-1, Sharp=0, Tough+2, Weird+2},
    {Charm+1, Cool-1, Sharp=0, Tough+2, Weird+1}}
%
\introductions{Outsider}
%
\history%
    {{They helped you at a critical point in your quest to find the truth. Tell them what you needed help with.},
    {They stood between you and what you needed to find out. Ask them why.},
    {They also lost a friend or relative to the paranormal. Ask them who it was.},
    {Relations, close or distant. Tell them exactly what.},
    {You respect their hard-earned knowledge, and often come to them for advice.},
    {They introduced you to the Bureau when you were learning the truth about the paranormal.},
    {They saw you absolutely lose it and go unhinged. Tell them what the situation was, and ask them how much collateral damage you caused.}}%
%
}{% -- pg.2/2 col.3/3
%
\levelingup
%
\improvementsonecol{%
    {Get +1 Tough, max +3.},
    {Get +1 Weird, max +3.},
    {Get +1 Cool, max +3.},
    {Get +1 Sharp, max +3.},
    {Take another Outsider move.},
    {Take another Outsider move.},
    {Take a move from another playbook.},
    {Take a move from another playbook.},
    {Gain an Astral Guide, like the Psychic has, and one of their Power moves.},
    {Gain another of the Psychic’s Power moves.}
}{%
    {Get +1 to any rating, max +3.},
    {Get back one used Luck point.},
    {Create a second Bureau Agent to play as well as this one.},
    {Mark two of the basic moves as advanced.},
    {Mark another two of the basic moves as advanced.},
    {Jump departments: change to a new playbook.},
    {Get promoted to the Head of Containment.  This character becomes an NPC.  Start a new character.},
    {Retire to safety.},
    {Resolve your first encounter. The Keeper makes the next mystery about this event, and should try to answer all remaining questions about it during the mystery (although there are sure to be new threads to investigate after...)}
}%
%
}%
% -- end playbook