%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Altered World Event of the Week is a Monster of the Week derivative.
%
% Much of the textual content in the playbooks is copied from the original playbooks,
% following approval by Michael Sands for the free distribution of the AWEotW document.
% See: https://genericgames.co.nz/third_party_policy/ for his third party policy.
%
% Re-use of this script is for personal reproduction of the formatting and generation
% of other custom playbooks.  Any reproduction of the text should seek approval per the
% aforementioned generic games third party policy.
%
% Monster of the Week is copyrighted by Evil Hat Productions, LLC and Generic Games.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% the psychic ---------------------------
%
% -- front page
%
\playbookpage{%
%
% -- pg.1/2 col.1/3
%
\pbcommon{Psychic}%
{I didn't choose to come here.  Something brought me.  Leading me every step of the way.  Tugging on my strings like I'm some kind of puppet.}%
{As you mark off your Luck boxes, your Astral Guide will get more demanding.}%
%
}{% -- pg.1/2 col.2/3
%
\moveexp{four}{Director}
\phantom{.}\\
%
\textit{Pick two of the four Power moves below.  These moves cannot be taken when leveling up unless specifically allowed (or your Keeper agrees).}\\
%
\begin{move}{Power: Psychic Whammy}
You can use your powers to \textbf{kick some ass}: roll +Weird instead of +Tough. The attack has 2-harm hand obvious ignore-armour. On a miss, you’ll get a psychic backlash
\end{move}%
\br[1mm]
%
\begin{move}{Power: Launch}
You can use your powers to levitate and throw objects with incredible force.  When you use launch to \textbf{kick some ass}: roll +Weird instead of +Tough.  The attack has 2-harm close obvious loud.  On a miss, you cause unintended collateral damage or put someone in danger.
\end{move}%
\br[1mm]
%
\begin{move}{Power: Shield}
When you use your powers to \textbf{protect someone} by forming a barrier with nearby objects, you gain 2-armour against any harm that is transferred to you. This doesn’t stack with your other armour, if any.
\end{move}%
\br[1mm]
%
\begin{move}{Power: Levitate}
You can quickly float up into the air, twenty feet or so, and hover there for a couple moments.  Eventually gravity will bring you back down, albeit very slowly.  Anytime you’re falling, you can control the rate at which you fall.  It’s not exactly the same as flying, but it’s as good as anyone else has ever done.
\end{move}%
\br[4mm]
%
\textit{Then pick two of these:}\\
%
\begin{move}{Telepathy}
You can read people’s thoughts and put words in their mind. This can allow you to \textbf{investigate a mystery} or read a bad situation without needing to actually talk. You can also manipulate someone without speaking. You still roll moves as normal, except people will not expect the weirdness of your mental communication.
\end{move}
%
}{% -- pg.1/2 col.3/3
%
\begin{move}{The Sight}
You can see the invisible, especially paranormal entities and influences. You may communicate with (maybe even make deals with) the paranormal forces you see, and they give you more opportunities to spot clues when you \textbf{investigate a mystery}.
\end{move}%
\br[1mm]
%
\begin{move}{Hunches}
\textbf{When something bad is happening} (or just about to happen) somewhere that you aren’t, roll +Sharp. On a 10+ you knew where you needed to go, just in time to get there. On a 7-9, you get there late—in time to intervene, but not prevent it altogether. On a miss, you get there just in time to be in trouble yourself.
\end{move}%
\br[1mm]
%
\begin{move}{Jinx}
You can \textbf{encourage coincidences to occur}, the way you want. When you jinx a target, roll +Weird. On a 10+ hold 2 and on a 7-9 hold 1. On a miss, the Keeper holds 2 over you to be used in the same way. Spend your hold to:
\holdoptions%
    {{Interfere with a bureau agent, giving them -1 forward.},
    {Help an agent, giving them +1 forward, by interfering with their enemy.},
    {Interfere with what a paranormal entity or object, or a bystander is trying to do.},
    {Inflict 1-harm on the target due to an accident.},
    {The target finds something you left for them.},
    {The target loses something that you will soon find.}}
\end{move}%
\br[2mm]
%
\begin{move}{Subdue}
When you \textbf{concentrate on taking control of a paranormally affected item or person} you may soothe or cleanse your target. Roll +Tough.  On a 10+ you get the effect you want.  On a 7-9 it takes a little while before it takes effect.  The paranormal presence has time to take one or two actions.  On a miss, something is preventing you from getting through to it.  That’s bad. 
\end{move}
%
}\pagebreak% -- back page
%
\playbookpage{%
%
% -- pg.2/2 col.1/3
%
\begin{move}{Third Eye}
When you \textbf{read a bad situation}, you can open up your third eye for a moment to take in extra information. Take +1 hold on any result of 7 or more, plus you can see invisible things. On a miss, you may still get 1 hold, but you’re exposed to supernatural danger. Unfiltered hidden reality is rough on the mind!
\end{move}
%
\begin{pbsect}{ASTRAL GUIDE}
Your powers have a source that is with you always, guiding you through the world.  It’s like a resonance, or a being in your dreams, or a flash of images and words inside your head.  It might be helping you because it likes you, or it might be driving you to pursue its own wants and goals.  Something like that.  Whatever, you barely understand it either.
\end{pbsect}%
\br[2mm]
%
\optionsparen{Signals from your Guide}{pick one}%
    {{A kaleidoscopic image that flashes through your vision.},
    {A creature who visits you in your head.},
    {A sudden urge to chant certain phrases.},
    {A disembodied voice talking to you in disjointed phrases.},
    {A vision from somewhere in the astral plane.}}%
\br[2mm]
The keeper can inject signals into the world as a sign that your source would like you to follow that path.  If you go where the signal wants you to, mark experience.  If you don’t, then your powers are unavailable until the end of the mystery (or until you cave).  As you mark off luck boxes, your guide will become pushier about getting you where it wants you to be.\\
%
\begin{pbsect}{TWO WAY COMMUNICATION}
\textbf{At the start of each mystery}, hold 2.  You can spend this hold anytime to send a message telepathically to your guide.  When you do, roll +Weird.  On a 10+, your guide reveals a key fact, clue, or location that will help you.  On a 7-9, the answer is clouded or difficult to interpret.  On a miss your guide’s reply is terrible, garbled, or somehow wrong.
\end{pbsect}
%
}{% -- pg.2/2 col.2/3
%
\optionsparen{Ratings}{pick one line}%
    {{Charm+1, Cool=0, Sharp+1, Tough-1, Weird+2},
    {Charm-1, Cool+1, Sharp=0, Tough+1, Weird+2},
    {Charm+2, Cool=0, Sharp-1, Tough-1, Weird+2},
    {Charm=0, Cool-1, Sharp+1, Tough+1, Weird+2},
    {Charm-1, Cool-1, Sharp+2, Tough=0, Weird+2}}
%
\introductions{Psychic}
\brln
%
\begin{history}
\begin{itemize}
\item They taught you to control your powers, to the extent that you can control them at all.
\item You are blood-kin. Decide together exactly what.
\item You are married, or romantically involved. Decide between you the exact relationship.
\item You’re old friends, and trust each other completely.
\item You used your powers on them one time. Decide if it was for selfish reasons or not, and tell them if they found out about it.
\item You’ve known each other some time, but since your powers manifested, you keep them at a distance emotionally.
\item You hope they can help you control your powers.
\item They saw you use your powers for selfish or vindictive reasons. Ask them who the victim was, and then tell them what you did.
\end{itemize}
\end{history}
%
}{% -- pg.2/2 col.3/3
%
\levelingup
%
\improvementsonecol{%
    {Get +1 Charm, max +3.},
    {Get +1 Weird, max +3.},
    {Get +1 Tough, max +3.},
    {Get +1 Sharp, max +3.},
    {Take another Psychic Power move.},
    {Take another Psychic or Psychic Power move.},
    {Take another Psychic move.},
    {Take a move from another playbook.},
    {Take a move from another playbook.},
    {You can use the Director’s Hotline.}
}{%
    {Get +1 to any rating, max +3.},
    {Get back one used Luck point.},
    {Create a second Bureau Agent to play as well as this one.},
    {Mark two of the basic moves as advanced.},
    {Mark another two of the basic moves as advanced.},
    {Get promoted somewhere in the Bureau.  This character becomes an NPC.  Start a new character.},
    {Retire to safety.},
    {Resolve the mystery of your Astral Guide. The Keeper makes the next mystery about this event, and should try to answer all remaining questions about it during the mystery (although there are sure to be new threads to investigate after).  Whether you keep your Guide and your powers depends on how the mystery gets resolved...}
}%
%
}%
% -- end playbook