% the ranger ---------------------------
%
% -- front page
%
\playbookpage{%
%
% -- pg.1/2 col.1/3
%
\pbcommon{Ranger}%
{Bureau leadership always goes on about how vital the secure and contain protocol is, how it's our duty to protect these things.  Bullshit.  I protect us.}%
{When you spend a point of luck, the Keeper will bring about some danger or complication to one of your squad members.}%
%
}{% -- pg.1/2 col.2/3
%
\moveexp{four}{Ranger}
\br[1mm]
%
\textit{Pick three of these:}\\
%
\begin{move}{Bottle It Up}
If you want, you can take up to +3 bonus when you \textbf{act under pressure}. For each +1 you use, the Keeper holds 1. That hold can be spent later—one for one—to give you -1 on any move except act under pressure.
\end{move}%
\br[1mm]
%
\begin{move}{Unfazeable}
Take +1 Cool (Max +3).
\end{move}%
\br[1mm]
%
\begin{move}{Battlefield Awareness}
You always know what’s happening around you, and what to watch out for. Take +1 armour (max 2-armour) on top of whatever you get from your gear.
\end{move}%
\br[1mm]
%
\begin{move}{Leave No One Behind}
In combat, when you \textbf{help someone escape}, roll +Sharp. On a 10+ you get them out clean. On a 7-9, you can either get them out or suffer no harm, you choose. On a miss, you fail to get them out and you’ve attracted hostile attention.
\end{move}%
\br[1mm]
%
\begin{move}{Tactical Genius}
When you \textbf{read a bad situation}, you may roll +Cool instead of +Sharp.
\end{move}%
\br[1mm]
%
\begin{move}{Medic}
You have a full first aid kit, and the training to heal people. When \textbf{you do first aid}, roll +Cool. On a 10+ the patient is stabilized and healed of 2 harm. On a 7-9 choose one: heal 2 harm or stabilize the injury. On a miss, you cause an extra 1 harm. This move takes the place of regular first aid.
\end{move}%
\br[1mm]
%
\begin{move}{Trust Me}
When you \textbf{tell a normal person the truth in order to protect them from danger}, roll +Charm. On a 10+ they’ll do what you say they should, no questions asked. On a 7-9 they do it, but the Keeper chooses one from:
\holdoptions%
    {They ask you a hard question first.,
    They stall and dither a while.,
    They have a “better” idea.}%
    On a miss, they’re going to think you’re crazy and probably dangerous too.
\end{move}
%
}{% -- pg.1/2 col.3/3
%
\textit{And you get this one:}\\
%
\begin{move*}{Call For Backup}
When you \textbf{deal with the Bureau}, requesting help or gear, or making excuses for a failure, roll +Sharp. On a 10+, you’re good—your request for gear or personnel is okayed, or your slip-up goes unnoticed. On a 7-9, things aren’t so great. You might get chewed out by your superiors and there’ll be fallout, but you get what you need for the job. On a miss, you screwed up: you might be suspended or under investigation, or just in the doghouse. You certainly aren’t going to get any help until you sort it all out.
\end{move*}
%
\begin{pbsect}{GEAR}
Pick one heavy weapon, two normal weapons, a vehicle, and describe your squad.  You get either a flak vest (1-armour hidden) or combat armor (2-armour heavy) for protection.
\end{pbsect}
\br[2mm]
%
\optionsparen{Heavy Weapons}{choose one}%
    {Assault rifle (3-harm far area loud reload),
    Grenade launcher (4-harm far area messy loud reload),
    Sniper rifle (4-harm far),
    Grenades (4-harm close area messy loud),
    Submachine gun (3-harm close area loud reload)}
\brln
%
\optionsparen{Normal Weapons}{choose two}%
    {.38 revolver (2-harm close reload loud)1,
    9mm (2-harm close loud),
    Hunting rifle (2-harm far loud),
    Shotgun (3-harm close messy),
    Big knife (1-harm hand)}%
%
}\pagebreak% -- back page
%
\playbookpage{%
%
% -- pg.2/2 col.1/3
%
\begin{pbsect}{YOUR SQUAD}[]
You don’t work alone, you’re one part of a highly trained team of operatives.
\end{pbsect}
%
\begin{pbsect}{VEHICLE}
The bureau provides your squad with an outfitted truck, van, or car built for handling AWEs. Choose two good things and one bad thing about it.
\br[2mm]
\textit{Good things}: roomy; surveillance gear; fast; stealthy; intimidating; classic; medical kit; sleeping space; toolkit; concealed weapons; anonymous; armoured (+1 armour inside); tough; paranormal item container.
\br[2mm]
\textit{Bad things}: loud; obvious; temperamental; beaten-up; gas-guzzler; uncomfortable; slow; old.
\end{pbsect}
%
\begin{pbsect}{SQUAD MEMBERS}
Your squad consists of two, three, or four members (including yourself).  Name each member, give them a specialty and a flaw from the list, and write a sentence about your relationship.
\br[2mm]
\textit{Specialties}: driver; medic; strategy and tactics; sniper; demolitions; paranormal containment; psychic; veteran; hacker; stealthy; heavy weapons.
\br[2mm]
\textit{Flaws}: green; aggro; callous; bossy; paranoid; compromised; addict; strict; short-sighted; bad aim.
\end{pbsect}%
\brln
%
\begin{blurb}{Squad Member 1:}
\vspace{3pt}
Specialty: \rule{0.3\linewidth}{0.5pt} Flaw: \rule{0.3\linewidth}{0.5pt}
\br[1mm]
Relationship: \rule{0.675\linewidth}{0.5pt}
\br[1mm]
Tags: \rule{0.825\linewidth}{0.5pt}
\end{blurb}%
\br[4mm]
%
\begin{blurb}{Squad Member 2:}
\vspace{3pt}
Specialty: \rule{0.3\linewidth}{0.5pt} Flaw: \rule{0.3\linewidth}{0.5pt}
\br[1mm]
Relationship: \rule{0.675\linewidth}{0.5pt}
\br[1mm]
Tags: \rule{0.825\linewidth}{0.5pt}
\end{blurb}%
\br[4mm]
%
\begin{blurb}{Squad Member 3:}
\vspace{3pt}
Specialty: \rule{0.3\linewidth}{0.5pt} Flaw: \rule{0.3\linewidth}{0.5pt}
\br[1mm]
Relationship: \rule{0.675\linewidth}{0.5pt}
\br[1mm]
Tags: \rule{0.825\linewidth}{0.5pt}
\end{blurb}
}{% -- pg.2/2 col.2/3
%
\optionsparen{Ratings}{pick one line}%
    {{Charm=0, Cool+2, Sharp-1, Tough+2, Weird-1},
    {Charm-1, Cool+2, Sharp+1, Tough+1, Weird=0},
    {Charm+1, Cool+2, Sharp+1, Tough-1, Weird=0},
    {Charm-1, Cool+2, Sharp+1, Tough=0, Weird+1},
    {Charm=0, Cool+2, Sharp+2, Tough-1, Weird-1}}
%
\introductions{Ranger}%
\brln
%
\history%
    {{You went through hell together: maybe an AWE, maybe military service, maybe time in an institution. Whatever it was, it bound you together, and you have total trust in each other.},
    {Your relationship with them has romantic potential. So far it hasn’t gone further.},
    {They’re on the Bureau’s internal watch list, and you’ve been keeping an eye on them.},
    {You are related. Tell them how close.},
    {You met on a mission and worked together unofficially. And successfully.},
    {You were friends back in training, before the Bureau recruited you. This could be military, law enforcement, or some weirder school: decide the details between you.},
    {They pulled you (and maybe your team) out of a terrible FUBARed mission.},
    {You got sent to “deal with them” as a hazard to the Bureau’s policies one time. Tell them how you resolved this.}}%
%
}{% -- pg.2/2 col.3/3
%
\levelingup
%
\improvementsonecol{%
    {Get +1 Charm, max +3.},
    {Get +1 Cool, max +3.},
    {Get +1 Sharp, max +3.},
    {Get +1 Tough, max +3.},
    {Take another Ranger move.},
    {Take another Ranger move.},
    {Take a move from another playbook.},
    {Take a move from another playbook.},
    {Pick another Serious Weapon.},
    {Add another good tag to your vehicle or change the bad tag.},
    {Add someone to your squad.}
}{%
    {Get +1 to any rating, max +3.},
    {Get back one used Luck point.},
    {Pick a squadmate as a second Bureau Agent to play as well as this one.},
    {Mark two of the basic moves as advanced.},
    {Mark another two of the basic moves as advanced.},
    {Jump departments: change to a new playbook.},
    {Get promoted to the Head of Operations.  This character becomes an NPC.  Start a new character.},
    {Retire to safety.}
}%
%
}%
% -- end playbook