%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Altered World Event of the Week is a Monster of the Week derivative.
%
% Much of the textual content in the playbooks is copied from the original playbooks,
% following approval by Michael Sands for the free distribution of the AWEotW document.
% See: https://genericgames.co.nz/third_party_policy/ for his third party policy.
%
% Re-use of this script is for personal reproduction of the formatting and generation
% of other custom playbooks.  Any reproduction of the text should seek approval per the
% aforementioned generic games third party policy.
%
% Monster of the Week is copyrighted by Evil Hat Productions, LLC and Generic Games.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% the researcher ---------------------------
%
% -- front page
%
\playbookpage{%
%
% -- pg.1/2 col.1/3
%
\pbcommon{Researcher}%
{Given the choice, tell me which option would you pick: a lab for testing human blood samples, or a lab for testing an interdimensional, creeping fungus?}%
{When you spend a point of luck, something inside your lab goes awry or missing.}%
%
}{% -- pg.1/2 col.2/3
%
\moveexp{two}{Researcher}%
%
\begin{move}{I've Read About This Sort of Thing}
Roll +Sharp instead of +Cool when you \textbf{act under pressure}.
\end{move}%
\br[1mm]
%
\begin{move}{Often Right}
When an \textbf{agent comes to you for advice} about a problem, give them your honest opinion and advice. If they take your advice, they get +1 ongoing while following your advice, and you mark experience.
\end{move}%
\br[1mm]
%
\begin{move}{Preparedness}
When you \textbf{need something unusual or rare}, roll +Sharp. On a 10+, you have it here right now. On a 7-9 you have it, but not here: it will take some time to get it. On a miss, you know where it is, but it’s somewhere real bad.
\end{move}%
\br[1mm]
%
\begin{move}{The Person With The Plan}
\textbf{At the beginning of each mystery}, roll +Sharp. On a 10+ hold 2, on a 7-9 hold 1. Spend the hold to be where you need to be, prepared and ready. On a miss, the Keeper holds 1 they can spend to put you in the worst place, unprepared and unready.
\end{move}%
\br[1mm]
%
\begin{move}{Dark Past}
If \textbf{you trawl through your memories} for something relevant to the case at hand, roll +Sharp. On a 10+ ask the Keeper two questions from the list below. On a 7-9 ask one. On a miss, you can ask a question anyway but that will mean you were personally complicit in creating the situation you are now dealing with. The questions are:
\holdoptions%
    {{When I last dealt with this paranormal event (or one of its kind), what did I learn?},
    {What research do I know that could help here?},
    {Do I know anyone who might be behind this?},
    {Who do I know who can help us right now?}}
\end{move}%
%
}{% -- pg.1/2 col.3/3
%
\begin{move}{Ritual Experiments}
When you \textbf{perform an experiment on an altered item} you can treat that act as something the item needs or wants.  Roll +Tough.  On a 10+ the item is subdued for a time.  On a 7-9 the item reacts negatively to the experiment, but you’re ready for it.  On a miss, that wasn’t at all what the item wanted, and now you’re stuck with it and its erratic behavior.
\end{move}%
\br[1mm]
%
\begin{move}{Helping Hands}
You have a lab assistant whose job is to help you out with whatever you need.  When \textbf{you put your assistant in danger} in the name of science, roll +Charm.  10+ they’re fine, and besides this is how real science happens, they should get used to it.  7-9 pick one:
\holdoptions%
    {{They get hurt in the process.},
    {They complain to someone important about what they’re going through.},
    {Whatever you’re researching gets damaged or set loose.}}%
On a miss, prepare for the worst.
\end{move}%
\br[1mm]
%
\begin{move}{Work From Anywhere}
You have a tiny, mobile lab built into a van, moving truck, trailer, or shipping container.  Pick one of your three lab options.  That part of your lab is accessible wherever you are, no matter where you are, provided that the vehicle which carries it can make it there.
\end{move}%
\br[1mm]
%
%
}\pagebreak% -- back page
%
\playbookpage{%
%
% -- pg.2/2 col.1/3
%
\begin{pbsect}{RESEARCH LAB}[]
You have a personal lab, a safe place to work, inside the Bureau's headquarters. Pick three of the options below for your lab:
\end{pbsect}
\br[2mm]
%
\textbf{Published Research}: You have access to extensive publications on paranormal events.  When you spend some time studying the literature, take +1 forward to investigate the mystery.
\br[2mm]
\textbf{Ritual Research}: You have access to extensive documentation on previously successful rituals.  When you refer to these documents, describe a past event where a similar paranormal event, item, or entity was successfully contained, then take +1 forward on Ritual or Fringe Science.
\br[2mm]
\textbf{Reinforced Container}: Your lab has a reinforced room that can contain destructive paranormal items and entities without too much worry of them breaking out.
\br[2mm]
\textbf{Infirmary}: You can relieve people of paranormal influence, and have the space for one or two to recuperate.  The Keeper will tell you how long any patient’s recovery is likely to take, and if you need extra supplies or help.
\br[2mm]
\textbf{Workshop}: You have a space for constructing and repairing gadgets and paranormal equipment.  Work out with the keeper how long any repair or construction will take, and if you need extra supplies and help.
\br[2mm]
\textbf{Black Rock Walls}: This room is isolated from every kind of paranormal influence that you know about. Anything you stash in there can’t be found, can’t affect anything outside the lab, and can’t get out without some destruction.
\br[2mm]
\textbf{Safe Room}: Your lab comes with a safe room that is protected by normal and paranormal means.  You and up to two others can hide out there for a few days, safe from pretty much everything.
\br[2mm]
\textbf{Ritual Laboratory}: Your lab is equipped with all kinds of weird tools and supplies useful for doing rituals (like the move Ritual or Grand Ritual).
%
}{% -- pg.2/2 col.2/3
%
\optionsparen{Ratings}{pick one line}%
    {{Charm-1, Cool+1, Sharp+2, Tough+1, Weird=0},
    {Charm=0, Cool+1, Sharp+2, Tough-1, Weird+1},
    {Charm+1, Cool-1, Sharp+2, Tough+1, Weird=0},
    {Charm-1, Cool+1, Sharp+2, Tough=0, Weird+1},
    {Charm-1, Cool=0, Sharp+2, Tough-1, Weird+2}}
%
\introductions{Researcher}
\brln
%
\begin{history}%
\begin{itemize}
\item They are your student, apprentice, assistant, ward, or child. Between you, decide which.
\item They came to you for advice, and your advice got them out of trouble. Ask them what the trouble was.
\item They know about some of your unethical research, but they’ve agreed to keep quiet about them. Tell them what they know.
\item A distant relation. Tell them exactly what.
\item You were previously both members of an eldritch group, now disbanded. Ask them why they left, then tell them why you did.
\item They once helped you get a singular item that is now in your lab. Tell them what it was.
\item You both had to deal with the former head of research, who went crazy or whose obsessions got too extreme. Ask them how it ended.
\item You saved their life in a tight spot. Tell them what happened
\end{itemize}
\end{history}%
%
}{% -- pg.2/2 col.3/3
%
\levelingup
%
\improvementsonecol{%
    {Get +1 Charm, max +3.},
    {Get +1 Weird, max +3.},
    {Get +1 Cool, max +3.},
    {Get +1 Sharp, max +3.},
    {Take another Researcher move.},
    {Take another Researcher move.},
    {Add an option to your Lab.},
    {Add an option to your Lab, or add a second option to your Remote Lab.},
    {Take a move from another playbook.},
    {Take a move from another playbook.}
}{%
    {Get +1 to any rating, max +3.},
    {Get back one used Luck point.},
    {Create a second Bureau Agent to play as well as this one.},
    {Mark two of the basic moves as advanced.},
    {Mark another two of the basic moves as advanced.},
    {Jump departments: change to a new playbook.},
    {Get promoted to the Head of Research.  This character becomes an NPC.  Start a new character.},
    {Retire to safety.}
}%
%
}%
% -- end playbook